---
title: "Palmer's Penguins"
format: html
editor: visual
---

## Initilization

```{r}
#| warning: false

library(tidyverse)
library(palmerpenguins)
```

```{r}
#| warning: false
penguins

View(penguins)
```

# Single trait distribution

This shows the bill length of three penguin species. it shows that the mean bill length of chinstrap penguins are the longest, and adelie is the shortest.

```{r}
  #| warning: false

ggplot(data=penguins) +
  geom_boxplot(mapping= aes(x=species, y=bill_length_mm,fill=species))+
  #remove the legend
  theme(legend.position = "none")
```

Body mass for three different species of penguin.

```{r}
#| warning: false
ggplot(data=penguins) +
  geom_jitter(mapping= aes(x=species, y=body_mass_g,))
```

# Relationship between multiple traits

Flipper length as a function of body mass for three species of penguin, color indicates sex.

```{r}
#| warning: false
ggplot(data=penguins) +
  geom_point(mapping= aes(x=body_mass_g, y=flipper_length_mm, color=sex))+
  facet_wrap(~species)+
  theme_minimal()
```

Flipper length as a function of body mass for three species of penguin on three different islands.

```{r}
#| warning: false
ggplot(
  data = penguins,
  mapping = aes(x = body_mass_g, y = flipper_length_mm, color = species)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap( ~ island) +
  theme_minimal()
```

# Sexual dimorphism

Here I have removed NA values so that there are only Males and Females box plots, and plotted the bill length by species with sex separated per species.

```{r}
#| warning: false
penguins %>% 
drop_na() %>% 
ggplot() +
  geom_boxplot( aes(x=species, y=bill_length_mm, fill=sex))+
  theme_minimal()
```

Body mass of the three penguin species, color indicates sex.

```{r}
#| warning: false

ggplot(data=penguins) +
  geom_jitter(mapping= aes(x=species, y=body_mass_g,color=sex))
```
